Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-10 paper/paper.tex
pass on prio and clusterization

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use support. We decided to discard those. For example, many
tests we found required a Node.js runtime~\cite{node} for
execution. The main source of test cases is the official
Test262~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}. This test suite contains 87\% of
all the tests we used. We also considered test suites of three of the
four engines mentioned in Section~\ref{sec:methodology:engines} and
four other engines. Table~\ref{tab:test-suites} shows the breakdown of
tests we considered. Column ``original'' shows the test cases for each
test suite. Overall, we found a total of \totfiles{} JS files. We did
not consider tests from the \chakra{} repository because they depend
on non-portable objects. Notice that the number of tests in
\veight\ is low. That happens because many tests in \veight{} are
inherited from Mozilla and \jsc{}; we discarded those to avoid
repetition and to give credit where it is due. Column
``compile-in-all'' shows the number of test cases for which all four
engines we analyzed do not throw compile-time error. We discarded
tests that manifest compile errors as they clearly indicate missing
features; these tests use non-portable names (\eg{}, \jsc{}'s
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, although being part of the spec, not all
engines currently support. Finally, column ``no-fail-in-all'' shows
the tests for which all engines
pass. Section~\ref{sec:transplantation} discusses these failures, some
of which are indicative of bugs. The tests under this column will be
used to create new, potentially fault-revealing, tests. For that, it
is important to assure that all of them pass.

@@

Figure~\ref{fig:workflow} illustrates the infrastructure we used for
differential testing, use in part of our study. The bug-finding
process takes on input JS files from regression test suites of various
JS engines and generates warnings on output. Boxes in the figure
denote encapsulation; arrowed lines indicate data flow. The cycle
icons denote repetition--the leftmost icon indicates that each file in
the input list will be analyzed in separate whereas the rightmost icon
shows that a single file will be fuzzed multiple times.

@@

The bug-finding process works as follows. New inputs are obtained for
a given test input using some off-the-shelf input
fuzzer~\cite{fuzz-testing-history}.\Comment{ Several fuzzing methods
  have been proposed in the past, varying with respect to how new
  inputs are
  generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}
Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
The oracle checks whether or not the output produced for the fuzzed
file is consistent across all engines. In case the test passes in all
engines or fails in all engines (\ie{}, the output is consistent), the
infrastructure discards the test. Otherwise, it considers the input as
potentially fault-revealing; hence interesting for human
inspection. Note that a number of reasons exist, other than a bug, to
explain discrepancy (see Table~\ref{tab:false-positives}). We used the
open-source eshost-cli project~\cite{eshost-cli}, also used at
Microsoft, for checking output discrepancy.

@@

Recall that a warning can be manifested for reasons other than a bug
and there is no clear way to distinguish those cases automatically (see
Table~\ref{tab:false-positives}). A human needs to inspect the warning
to diagnose the discrepancy. To facilitate inspection, the
infrastructure prioritize these warnings and clusters them in
groups. Considering prioritization, we classified warnings in two
kinds, reflecting their likelihood to manifest a real bug. Warnings of
the kind ``\hi{}'' are associated with the cases where the test code
executed to completion without violating any internal checks but it
violated assertions declared in the test itself or its harness. The
rationale is that the input is valid--considering the checks declared
in the API functions--but, still, it manifests discrepancy through
violation of an assertion declared in the test.\Mar{example!} In contrast, warnings
in the ``\lo{}'' group reflect the cases where the anomaly was
observed during the execution of functions not related to the test
itself. We found that different engines often check pre-conditions of
those functions differently. It can happen, for example, that one
engine enforces a weaker pre-condition on a function input compared to
another engine and that is acceptable.\Mar{example!} In those cases, our infrastructure would
observe a discrepancy that is more likely to be associated with an
invalid input produced by the fuzzer, \ie{}, it is likely to be a bug
in the test code not the engine (library or runtime) code. Although we
did find real bugs from ``\lo{}'' warnings, the proportion was much
lower compared to ``\hi{}'' warnings. Overall, only \Fix{12\%} of the
reals bugs we found originated from ``\lo{}'' warnings.

@@

>>>>

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use support. We decided to discard those. For example, many
tests we found required a Node.js runtime~\cite{node} for
execution. The main source of test cases is the official
Test262~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}. This test suite contains 87\% of
all the tests we used. We also considered test suites of three of the
four engines mentioned in Section~\ref{sec:methodology:engines} and
four other engines. Table~\ref{tab:test-suites} shows the breakdown of
tests we considered. Overall, we found a total of \totfiles{} JS
files. Column ``original'' shows the test cases for each
test suite. We did not consider tests from the \chakra{} repository because they depend
on non-portable objects and notice that the number of tests in
\veight\ is low. That happens because many tests in \veight{} are
inherited from Mozilla and \jsc{}; we discarded those to avoid
repetition and to give credit where it is due. Column
``compile-in-all'' shows the number of test cases for which all four
engines we analyzed do not throw compile-time error. We discarded
tests that manifest compile errors as they clearly indicate missing
features; these tests use non-portable names (\eg{}, \jsc{}'s
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, although being part of the spec, not all
engines currently support. Finally, column ``no-fail-in-all'' shows
the tests for which all engines
pass. Section~\ref{sec:transplantation} discusses these failures, some
of which are indicative of bugs. The tests under this column will be
used to create new, potentially fault-revealing, tests. For that, it
is important to assure that all of them pass.

@@

@@

Figure~\ref{fig:workflow} illustrates the infrastructure for
differential testing, which is used in part of this study. It takes on
input a list of JS files and generates warnings on output. Boxes in
the figure denote encapsulation, arrowed lines denote data flow, and
the cycle icons denote repetition--the leftmost icon indicates that
each file in the input list will be analyzed in separate whereas the
rightmost icon shows that a single file will be fuzzed multiple times.
The bug-finding process works as follows. New inputs are obtained for
a given test input using some off-the-shelf input
fuzzer~\cite{fuzz-testing-history}.\Comment{ Several fuzzing methods
  have been proposed in the past, varying with respect to how new
  inputs are
  generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}
Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
The oracle checks whether or not the output produced for the fuzzed
file is consistent across all engines. In case the test passes in all
engines or fails in all engines (\ie{}, the output is consistent), the
infrastructure discards the test. Otherwise, it considers the input as
potentially fault-revealing; hence interesting for human
inspection. Note that a number of reasons exist, other than a bug, to
explain discrepancy (see Table~\ref{tab:false-positives}). We used the
open-source eshost-cli project~\cite{eshost-cli}, also used at
Microsoft, for checking output discrepancy.

@@

Recall that a warning can be manifested for reasons other than a bug
and there is no clear way to distinguish those cases automatically (see
Table~\ref{tab:false-positives}). A human needs to inspect the warning
to diagnose the discrepancy. To facilitate inspection, the
infrastructure prioritize these warnings and clusters them in
groups.

\subsection{Prioritization}

Considering prioritization, we classified warnings in two kinds,
reflecting their likelihood to manifest a real bug. Warnings of the
kind ``\hi{}'' are associated with the cases where the test code
executed to completion without violating any internal checks but it
violated assertions declared in the test itself or its harness. The
rationale is that the input is more likely to be valid as it it did
not raise exceptions during the execution of the application code,
but, it manifests discrepancy through violation of an assertion
declared in the test. In contrast, warnings in the ``\lo{}'' group are
more likely to be asssociated with invalid inputs. They reflect the
cases where the anomaly is observed during the execution of functions
not related to the test itself. We found that different engines often
check pre-conditions of those functions differently. It can happen,
for example, that one engine enforces a weaker pre-condition on a
function input compared to another engine and that is acceptable. In
those cases, the infrastructure would observe a discrepancy that is
more likely to be associated with an invalid input produced by the
fuzzer, \ie{}, it is likely to be a bug in the test code not the
engine (library or runtime) code. Although we did find real bugs from
``\lo{}'' warnings, the proportion was much lower compared to
``\hi{}'' warnings. Overall, only \Fix{12\%} of the reals bugs we
found with fuzzing originated from ``\lo{}'' warnings. \Fix{quickly
  explain why LO can still be a bug.}

\subsection{Clusterization}

@@

Figure~\ref{fig:err-messages} shows the error messages produced by a
\lo warning. Note that all message appear to be related to the same
problem.

\begin{figure}[h]
\begin{tabular}{ll}
\veight{} & ``Unexpected end of input''\\
\jsc{} & ``Unexpected end of script''\\
\smonkey{} & ``Expected expression, got end of script''
\end{tabular}
\caption{\label{fig:err-messages}Example error messages associated
  with a \lo{} warning. In this case, the test passes in \chakra.}
\end{figure}
